Gaudeamus Figures

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

```{r, echo=FALSE, message=FALSE}
library(dplyr)
dfo <- readRDS("df.Rds")
```

```{r Gaudeamus_Vaasa, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
df <- df %>% filter(!is.na(publication_year))
tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)

@@

>>>>

```{r, echo=FALSE, message=FALSE}
library(dplyr)
knitr::opts_chunk$set(fig.path = "figure_Gaudeamus/", dev="CairoPNG")
dfo <- readRDS("df.Rds")
```

```{r Vaasa, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
place <- "Vaasa"
miny <- 1764
maxy <- 1917
df <- df %>% filter(!is.na(publication_year)) %>%
             filter(publication_year >= miny & publication_year <= maxy)
tmp1 <- df %>% filter(publication_place == place) %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)

@@

```{r Turku, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
place <- "Turku"
miny <- 1640
maxy <- 1917
df <- df %>% filter(!is.na(publication_year)) %>%
             filter(publication_year >= miny & publication_year <= maxy)
tmp1 <- df %>% filter(publication_place == place) %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)

```{r Helsinki, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
place <- "Helsinki"
miny <- 1746
maxy <- 1917
df <- df %>% filter(!is.na(publication_year)) %>%
             filter(publication_year >= miny & publication_year <= maxy)
tmp1 <- df %>% filter(publication_place == place) %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)

```{r Suomi, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
place <- "Finland"
miny <- 1640
maxy <- 1917
df <- df %>% filter(!is.na(publication_year)) %>%
             filter(publication_year >= miny & publication_year <= maxy)
tmp1 <- df %>% filter(publication_country == place) %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)
